RELATION BETWEEN STAR FORMATION RATE, GAS MASS AND STELLAR MASS IN THE ANDROMEDA GALAXY

### 2015-03-24 draft3.tex
This is the final one so far

%P5(2*): What we did and why Andromeda and
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). %We used three different gas maps and SFR maps, to identify if any of these laws work better with specific gas mass or SFR tracer. 
Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of the galaxy or not. Since, M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
%PB: Give a little more detail in the following sentence

@@

\subsection{Visible light}
Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission. \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope. \halpha maps, which were obtained from the NOAO science archive are available in 10 overlapping fields. We created a Mosaic image of the maps using Montage. Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}. We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure ~\ref{fig:halpha}). Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.

@@

Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit. Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other, 
%PB: the two parts of the sentence above ("similarity of results" and "in close agreement") seem to say the same thing -- or am I not understanding what you mean here?
We only interpret the results from the SFR(FUV+24$\mu$m). Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}. %In this section we are going to talk about result from fitting the K-S Law, results from fitting the extended Schmidt law and the comparison between these two star formation laws and which one works better in the M31. %SR: Should I keep that or not
%PB: I don't think you need the "In this section" sentence; the content is clear from the subsection headings.

\subsection{The K-S law in M31}

>>>>

%P5(2*): What we did and why Andromeda and
In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31). %We used three different gas maps and SFR maps, to identify if any of these laws work better with specific gas mass or SFR tracer. 
Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of the galaxy or not. The M31 is the nearest spiral galaxy to the Milky Way. Therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
%PB: Give a little more detail in the following sentence

@@

\subsection{Visible light}
Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission. \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope. \halpha maps, which were obtained from the NOAO science archive are available in 10 overlapping fields. We created a Mosaic image of the maps using Montage \citep{Berriman08}. Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}. We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure ~\ref{fig:halpha}). Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.

@@

Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit. Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other, 
%PB: the two parts of the sentence above ("similarity of results" and "in close agreement") seem to say the same thing -- or am I not understanding what you mean here?
We only interpret the results from the SFR(FUV+24$\mu$m). Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
\subsection{The K-S law in M31}
